\documentclass[a4paper,10pt]{article}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{fontenc}
\usepackage{graphicx}

\usepackage[dvips]{hyperref}

\usepackage{eventB}

\title{Requirements Document\\ProvenLift}
\author{Adrian Friedli\\Alexander Bernauer}

\begin{document}
\maketitle
\newpage

\section{Environmental Assumptions}

First, we enumerate all entities which are relevant to the system.

\env{There is an elevator with a door, a door engine and a cable engine.}
\env{There is a controller which executes the system.}
\env{There is a sequence of N+1 floor which are indexed from 0 to N. The floor with index 0 is at the bottom and the floor with index N is at the top.}
\env{On every floor except the one with index N there is a up-button. On every floor except the one with index 0 there is a down-button.}
\env{In the elevator there are N+1 so called floor buttons indexed from 0 to N.}
\env{For every botton there is a light.}

All the entities have different possible states.
\env{The elevator is either stopped, moving up or moving down.}
\env{The cable engine is either stopped, winding or unwinding.}
\env{The door engine is either opening, closing or stopped.}
\env{The door can be fully open, half open or closed.}
\env{Every button can be pressed or not pressed.}
\env{Every light is either on or off.}

Here are some basic relationships between the entities of the system.
\env{The elevator is either between two consequtive floors or at one floor.}
\env{If the door engine is opening the door status changes from closed to half open and/or from half open to open. If the door engine is closing the door status changes from open to half open and/or from half open to closed. If the door engine is stopped the door status does not change.}
\env{If the cable motor is stopped the elevator is stopped. If the cable motor is winding the elevator moves up. If the cable motor is unwinding the elevator moves down.}

Now we list all input information.
\env{For each entity except the lights there is a sensor which measures the state of the entity.}
\env{There is a sensor, called floor sensor, which measures the index of the floor if the elevator is at that floor. If the elevator is between two floors, the sensor measures the value -1.}

This interconnects the whole system.
\env{The controler can send commands to the cable engine, the door engine and the lights of the buttons in order to alter their state.}
\env{The controller is connected to all buttons, sensors and engines in the system.}

\section{Functional Requirements}
This is the basic functionality of the system.
\fun{Users signal requests for a floor by pressing the corresponding buttons of that floor. Every request is eventually served as the elevator goes to the corresponding floor and opens the door.}
\fun{If all requests are served the elevator waits at the current floor for new requests.}

Now we describe the schedule which is used by the elevator to serve requests.
\fun{There is an elevator schedule which can be either waiting, up or down.}
\fun{The elevator schedule is set to waiting iff there is no request.}
\fun{If the elevator schedule is waiting and then a request for an upper/lower floor is signaled the elevator schedule is set to up/down.}
\fun{The elevator starts to move up/down only if the elevator schedule is up/down.}
\fun{The elevator stops at a floor iff there is a request for that floor.}
Once the elevator decided to schedule upwards it serves all upper floors until it starts to schedule downwards and vice versa.
\fun{The elevator schedule switches from up/down to down/up iff there is no request for a floor further up/down.}

These requirements handle the user interface.
\fun{If a button is pressed the corresponding light goes on.}
\fun{If the light corresponding to a floor button is on and the elevator is at the floor which corresponds to the button and the door is open, the light goes off.}
\fun{If the light corresponding to a down button is on and the elevator is at the floor which corresponds to the button and the elevator schedule is down and the door is open, the light goes off.}
\fun{If the light corresponding to a up button is on and the elevator is at the floor which corresponds to the button and the elevator schedule is up and the door is open, the light goes off.}

Finally, some security requirements.
\fun{When the cable engine is winding or unwinding then the door engine is closing.}
\fun{When the cable engine is winding or unwinding then the door is closed.}
\fun{If the elevator is between two floors the cable engine is not stopped.}
\fun{If the elevator is at the floor with index 0 the elevator will not move further down.}
\fun{If the elevator is at the floor with index N the elevator will not move further up.}

And of course, nobody want's to reboot the elevator ;-)
\fun{Once the system is started it never stops.}

\end{document}
